---
title: "Guided tutorials for ML summer"
author: "Danilo Sarti"
date: "6/20/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE)
```

```{r}
library(corrplot)
library(RColorBrewer)
require(GGally)
```


# Introduction to credit risk analysis: Would you give me some money?

* The data set default contains the following variables:  

```{r}
default <- readRDS("/Volumes/Dell Portab/talks_presentations/default.rds")
head(default)
```

* The data set reflects South America reality.

* This example is a very simple representation to what happens in reality. Banks use much more information!!

# We will calculate some correlations

```{r}
default$bsex=ifelse(default$sex=="F",1,0)
default$bregion=ifelse(default$region==2,1,0)
head(default)

ggpairs(default[,c(3,4,5,6,7,8)])


corrplot(cor(default[,c(3,4,5,6,7,8)]), type="upper", order="hclust",
         col=brewer.pal(n=8, name="RdYlBu"))
```

# Logistic Regression 

Logistic Regression is a ML procedure which helps us to predict the chances of something to happen or not! 


```{r}
mod1Logit<-glm(default~bsex+bregion+value_op+income+age,data=default,
             family=binomial("logit"))
summary(mod1Logit)
```

A second model!!

```{r}
mod2Logit<-glm(default~bsex+value_op,data=default,
             family=binomial("logit"))
summary(mod2Logit)

coef(mod2Logit)
```

Predicting some probabilities of default.

```{r}
## bsex=1 (woman) valueop=3000 
1/(1+exp(-(-1.0481021-1.1812830*1+0.0004319* 3000)))

## bsex=0 (man) valueop=3000 
1/(1+exp(-(-1.0481021-1.1812830*0+0.0004319* 3000)))
# with predict
newbsex=c(1,0) ## woman and man 
newvalueop=c(3000,3000)
predict(mod2Logit,newdata=data.frame(bsex=newbsex,value_op=newvalueop),type="response")

```

```{r}
require(erer)
mod2Logit<-glm(default~bsex+value_op,data=default,
             family=binomial("logit"),x=TRUE)
maBina(w=mod2Logit,digits=7) 
```



# Making some plots 

```{r}
with(data=default,plot(value_op,default,col="blue",xlim=c(0,7000),ylim=c(0,1)),ylab="prob")
## results regarding the women 
title(expression(paste(hat(P),"(default|sex,value_op) - mod2Logit")))
new_value_op=c(0,7000)
new_bsex=rep(1,length(new_value_op))
new_default<-predict(mod2Logit,newdata=data.frame(bsex=new_bsex,value_op=new_value_op),type="response")
lines(new_value_op,new_default,type="l",col="deeppink")
## resultados para os homens
new_bsex=rep(0,length(new_value_op))
new_default<-predict(mod2Logit,newdata=data.frame(bsex=new_bsex,value_op=new_value_op),type="response")
lines(new_value_op,new_default,col="blue")
```



# Neural Network

```{r}
# install package
#install.packages("neuralnet")
# load library
require(neuralnet)

# creating train set
def_train=default[c(1:180),]

# fit neural network
nn=neuralnet(default~bsex+bregion+value_op+income+age,data=def_train, hidden=3,act.fct = "logistic",
                linear.output = FALSE)


plot(nn)



```

Black: connections between layers and the weights on each connection. 

Blue: The bias term added in each step. 

```{r}
# creating test set
test=default[c(180:360),]
Predict=compute(nn,test)
head(Predict$net.result)
```


```{r}
#dev.off()
df=data.frame(test)
test$predicted=Predict$net.result
plot(test$value_op,test$predicted)
library(ggplot2)
ggplot(data=test, aes(x=value_op,y=predicted,col=as.factor(sex)))+geom_point()

```

